\documentclass[10pt, letter]{article}

\input{resume-preamble.tex}

% DOCUMENT
%\usepackage{layout}
%\begin{document}\layout
\begin{document}
\begin{center}
    {\LARGE Michael Sobrepera}\\[1mm]
    \href{mailto:mjsobrep@live.com}{mjsobrep@live.com}  |  (770) 324--6196  |  \href{https://michaelsobrepera.com}{michaelsobrepera.com}
    \end{center}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hrule
    \vspace{0cm}

\section*{Summary}
PhD student and full stack roboticist with background in medical device design and manufacturing. Innovating at the intersection of robotics, rehabilitation, and telemedicine.

\begin{cvsection}{Education}
    \cvitem{Doctor of Philosophy in Mechanical Engineering}{University of Pennsylvania}{Philadelphia, PA}{Aug 2016}{Expected Apr 2021}{Advisor: Dr.~Michelle Johnson}

    \cvitem{Master of Science in Robotics}{University of Pennsylvania}{Philadelphia, PA}{Aug 2016}{Aug 2019}{}
    %GPA: 3.32

    \cvitem{Bachelor of Science in Biomedical Engineering}{Georgia Institute of Technology}{Atlanta, GA}{Aug 2012}{Dec 2015}{Minor in Computer Science}
 %GPA: 3.35

    %\cvitem{Bachelor of Science in Chemical Engineering}{Auburn University Honors College}{Auburn, AL}{Aug 2011}{May 2012}{Pursued degree.}
 %GPA: 3.90
\end{cvsection}

\begin{cvsection}{Skills}

    \cvitemshort{Programming Languages}{Python, MATLAB, TypeScript, Arduino, LaTeX, SQL}{}

    \cvitemshort{Mechanical Design}{MCAD, Technical drawing, RTV molding, 3D printing, Classical machining}{}

    \cvitemshort{Software Infrastructure}{ROS, Docker, Git, NGINX, NodeJS, Redis, PostgreSQL, React}{}

\end{cvsection}


    \vspace{.2cm}
\begin{cvsection}{Experience}
    \cvitem{Doctoral Student Researcher / NIH F31 Fellow}{University of Pennsylvania, Rehabilitation Robotics Lab}{Philadelphia, PA}{Aug 2016}{present}{Developing an affordable socially assistive robot to aid in telepresence based assessment and treatment of patients with upper extremity motor impairments as a tool to expand the reach of clinicians while improving the objectivity of diagnostic tools.
The project involves two primary foci 1) understanding how patients react to telepresence robots which incorporate social robots and how that affects remote assessment and 2) developing a framework for identifying motor function from video of a patient doing various robot guided activities.}

    \cvitem{Research Technician II}{Georgia Institute of Technology, IRIM Technology Transition Lab}{Atlanta, GA}{Aug 2015}{June 2016}{Worked under Dr.\ Henrik Christensen and Dr.\ Larry Sweet to advance technologies in the visual servoing space, explicitly focused on potential industry applications. Refined an existing video based real-time textureless tracker from a research code base to a well documented robust system, to enable manipulation on non-fixed, non-located car parts at a client automotive facility. Utilized heavy industrial robots while developing perception, calibration, and control systems in C++ and Python. }

    \cvitem{Automation Intern}{Eli Lilly and Company}{Indianapolis, IN}{May 2015}{Aug 2015}{Evaluated options for offline software/hardware/operator in the loop plant simulations for the purposes of process validation, control code development, pre-Factory Acceptance Testing control system checkout, operator training, and process improvement, with a specific focus on Emerson DeltaV and Rockwell interoperability.}

    \cvitem{Machine Shop Supervisor}{Georgia Institute of Technology, TEP Machine Shop}{Atlanta, GA}{Aug 2014}{May 2015}{Maintained equipment, trained users, guided Masters in Biomedical Innovation and Development (MBID) students in design and prototyping of medical devices, supported research labs. }

    \cvitem{Product Development Engineering CO-OP}{Unilife Corporation}{York/King of Prussia, PA}{Jan 2014}{Jul 2014}{Worked throughout the product development pipeline on injectable drug delivery devices. Took products from customer needs through ideation, iterative prototyping, and pilot production. Worked on molding and assembly line design, procurement, assembly, and qualification. Developed test fixtures to ensure product quality.
    }

\end{cvsection}

\begin{cvsection}{Honors and Awards}
    \cvitemshort{National Science Foundation F31 Pre-doctoral Fellowship}{May 2020 -- Present}{}

    \cvitemshort{Wharton Entrepenuership Startup Challenge Innovation Prize}{May 2020}{}

    \cvitemshort{Rothberg Catalyzer First Place}{Nov 2019}{}

    \cvitemshort{University of Pennsylvania Fontaine Fellowship}{Sept 2016 -- Present}{}

    \cvitemshort{Hispanic Scholarship Fund (HSF) Scholar}{Dec 2016}{}

\end{cvsection}

\end{document}
